### 2020-12-16 treatise/2_problem_setting.tex
New DS narrow figures, OMP square figures

We restrict our consideration to the uniform linear array, which can be modeled as
%
\DispNum {a:y':VC:nh} {
\NC \V {a} \SB {\psi'}
\in \NC \MB {C} ^ {N_H} \NR
%
\NC \V {a} \SB {\psi'}
= \NC \F {1} {\R {N_H}} \sum_{n_h=0}^{N_H-1} \Ss {e} ^{\Ss {i} n_h \psi'} \V {u} _{n_h} \NR
}
%
where \m {\Ss {e}} is the base of natural logarithm, and \m {\Ss {i}} the imaginary unit.

@@

Recall that analog precoder is restricted to have value with magnitude being unity, i.e.,
%
\DispNum {F:R:1::R1} {
\NC \Nm {\M {F} _R} _{\SB {n_H, n_R}}
= \NC 1, \NR
%
\NC \Nm {\M {W} _R} _{\SB {n_R, n_H}}
= \NC 1, \NR
%
\NC n_H
= \NC 0, \dots N_H-1, \NR
%
\NC n_R
= \NC 0, \dots N_R-1 \NR
}
%
And we assume
%
\DispNum {N:H:NY:NY} {
\NC N_H \gg \NC N_R \NR
%
\NC N_R \gg \NC N_B \NR
}

@@

To convert the problem into a linear system recovery problem, we need several definitions.
%
\Result
{Definition}
{
Define \m {\Rm {vec} \SB {\M {A}} \in \MB {K} ^{N_1 \D N_2}} to be the vectorization of \m {\M {A} \in \MB {K} ^{N_1 \D  N_2}}.
Formally,
%
\DispNum {v:1:Am:N1} {
\NC \RB {\Rm {vec} \SB {\M {A}}} _{\SB {m}}
=\NC \M {A} _{\SB {m\; \Rm {Mod}}\; N_1, \Fl {m/N_1 }} \NR
}
%
The bijection is obvious, and we define \m {\Rm {vec} ^{-1}} so that
%
\DispNum {v:x:x::x:} {
\NC \Rm {vec} ^{-1} \SB {\Rm {vec} \SB {x}}
=\NC x \NR
}
}

@@

It would seem now appealing to write
%
\DispNum {h:h:ve:Nh} {
\NC \V {h}
:= \NC \Rm {vec} \SB {\M {H}}
\in \MB {C} ^{N_H^2} \NR
%
\NC \V {y}
:= \NC \Rm {vec} \SB {\M {Y}}
\in \MB {C} ^{N_B^2} \NR
%
\NC \V {z}
:= \NC \Rm {vec} \SB {\M {W} _B \M {W} _R \M {Z}}
\in \MB {C} ^{N_B^2} \NR
%
\NC \M {Q}
:= \NC \RB {\M {F} _B^\Tr \M {F} _R^\Tr} \otimes \RB {\M {W} _B \M {W} _R}
\in \MB {C} ^{N_B^2 \D N_H^2} \NR
}
%
to formulate our goal as sparse recovery problem of \m {\Rm {vec} \SB {\M {H}}} to be
%
\DispNum {y:y:Qh:hz} {
\NC \V {y}
=\NC \M {Q} \V {h} +\V {z} \NR
}
%
As we have motivated in previous sections, we want to use DS by considering sparse vector, and at the same time to get rid of the angle grid quantization problem.
However, there is no guarantee, though, that \m {\V {h}} will be sparse.

@@

\startsection [title={Angular space}]

Introduce the discrete Fourier transform matrix \m {\M {K}} defined to be
%
\DispNum {K:K:CN:H1} {
\NC \M {K} \in  \NC \MB {C} ^{N_H \D N_H} \NR
%
\NC \M {K} _{\SB {n_1, n_2}}
= \NC \F {1} {\R {N_H}} \Ss {e}^{2\pi \Ss {i} n_1 n_2 /N_H}, \NR
%
\NC \Q n_1, n_2
= \NC 0, 1, \dots, N_H-1 \NR
}
%
Sans serif \m {\Ss {e}} and \m {\Ss {i}} denote the natural base and imaginary unit, respectively.
Here recall that we have
%
\DispNum {K:K:I:::I} {
\NC \M {K}^\Adj \M {K}
= \NC \M {I} \NR
}
%
Observe that, if we write
%
\DispNum {G:G:KH:HK} {
\NC \M {G}
=\NC \M {K}^\Adj \M {H} \M {K} \NR
}
%
which has the interpretation as the angular space (i.e., spatial frequency domain) representation of \m {\M {H}}, then
%
\DispNum {Y:Y:WB:NY} {
\NC \M {Y}
=\NC \M {W} _B \M {W} _R \M {K} \D \M {G} \D \M {K}^\Adj \M {F} _R \M {F} _B
+\M {W} _B \M {W} _R \M {Z}
\in \MB {C} ^{N_B \D N_B} \NR
}
%
If at the end of day, \m {\M {G}} is sparse, then we recover \m {\M {G}} instead, and our use of DS is fully justified.
To simplify notation, set
%
\DispNum {P:P:FB:Nh} {
\NC \M {P}
:=\NC \RB {\M {F} _B^\Tr \M {F} _R^\Tr \M {K}^\ast} \otimes \RB {\M {W} _B \M {W} _R \M {K}}
\in \MB {C} ^{N_B^2 \D N_H^2} \NR
}
%
And accordingly
%
\DispNum {g:g:ve:Nh} {
\NC \V {g}
:= \NC \Rm {vec} \SB {\M {G}}
\in \MB {C} ^ {N_H \D N_H} \NR
}
%
Then
%
\DispNum {y:y:Pg:gz} {
\NC \V {y}
=\NC \M {P} \V {g} +\V {z} \NR
}

@@

If so, our program reads

\Result
{Algorithm}
{
\startitemize[n]
\item Let \m {\g_{\Rm {DS}} \geq 0} be given.
\item Input \m {\M {F} _B \in \NC \MB {C} ^{N_R \D N_B}},
\m {\M {F} _R \in \NC \MB {C} ^{N_H \D N_R}},
\m {\M {W} _R \in \NC \MB {C} ^{N_R \D N_H}},
\m {\M {W} _B \in \NC \MB {C} ^{N_B \D N_R}},
and \m {\M {Y} \in \NC \MB {C} ^{N_B \D N_B}}.
\item Find \m {\M {P} \in \MB {C} ^{N_B^2 \D N_H^2}}, \m {\V {y} \in \MB {C} ^{N_H^2}} as in above.
\item Calculate
%
\DispNum {g:g:mi:DS} {
\NC \Hat {\V {g}}
\LA \NC \startcases
\NC \Min {\V {g}' \in \MB {C} ^{N_H^2}}  \MC \VNm {\V {g}'} _1 \NR
%
\NC \Rm {subject} \; \Rm {to} \Q \MC \VNm {\M {P}^\Adj \RB {\V {y} -\M {P} \V {g}'}} _\infty \leq \g_{\Rm {DS}} \NR
\stopcases \NR
}
\item Convert \m {\Hat {\V {g}}} back to the space domain, namely
%
\DispNum {G:G:ve:1g} {
\NC \Hat {G}
\LA \NC \Rm {vec}^{-1} \SB {\Hat {g}} \NR
}
\item Recover the estimated \m {\Hat {\M {H}}}, as
%
\DispNum {H:H:KG:GK} {
\NC \Hat {\M {H}}
\LA \NC \M {K} \Hat {\M {G}} \M {K}^\Adj \NR
}
\item Output \m {\Hat {\M {H}}}.
\stopitemize
}

>>>>

We restrict our consideration to the uniform linear array, which can be modeled as
%
\DispNum {a:y':CN:NH} {
\NC \V {a} \SB {\psi'}
= \NC \F {1} {\R {N_H}} \sum_{n_h=0}^{N_H-1} \Ss {e} ^{\Ss {i} n_h \psi'} \V {u} _{n_h}
\in \MB {C} ^ {N_H} \NR
}
%
where \m {\Ss {e}} is the base of natural logarithm, and \m {\Ss {i}} the imaginary unit.

@@

Recall that analog precoder is restricted to have value with magnitude being unity, i.e.,
%
\DispNum {F:R:1::R1} {
\NC \Nm {\RB {\M {F} _R} _{\SB {n_H, n_R}}}
= \NC 1, \NR
%
\NC \Nm {\RB {\M {W} _R} _{\SB {n_R, n_H}}}
= \NC 1, \NR
%
\NC n_H
= \NC 0, \dots N_H-1, \NR
%
\NC n_R
= \NC 0, \dots N_R-1 \NR
}
%
And we assume
%
\DispNum {N:H:NY:NY} {
\NC N_H \gg \NC N_R \NR
%
\NC N_R \gg \NC N_B \NR
}

@@

We need several definitions.
%
\Result
{Definition}
{
Define \m {\Rm {vec} \SB {\M {A}} \in \MB {K} ^{N_1 \D N_2}} to be the vectorization of \m {\M {A} \in \MB {K} ^{N_1 \D  N_2}}.
Formally,
%
\DispNum {v:1:Am:N1} {
\NC \RB {\Rm {vec} \SB {\M {A}}} _{\SB {m}}
=\NC \M {A} _{\SB {m\; \Rm {Mod}}\; N_1, \Fl {m/N_1 }} \NR
}
%
The bijection is obvious, and we define \m {\Rm {vec} ^{-1}} so that
%
\DispNum {v:x:x::x:} {
\NC \Rm {vec} ^{-1} \SB {\Rm {vec} \SB {x}}
=\NC x \NR
}
}

@@

It would seem now appealing to write
%
\DispNum {h:h:ve:Nh} {
\NC \V {h}
:= \NC \Rm {vec} \SB {\M {H}}
\in \MB {C} ^{N_H^2} \NR
%
\NC \V {y}
:= \NC \Rm {vec} \SB {\M {Y}}
\in \MB {C} ^{N_B^2} \NR
%
\NC \V {z}
:= \NC \Rm {vec} \SB {\M {W} _B \M {W} _R \M {Z}}
\in \MB {C} ^{N_B^2} \NR
%
\NC \M {Q}
:= \NC \RB {\M {F} _B^\Tr \M {F} _R^\Tr} \otimes \RB {\M {W} _B \M {W} _R}
\in \MB {C} ^{N_B^2 \D N_H^2} \NR
}
%
to formulate the problem as a linear system:
%
\DispNum {y:y:Qh:hz} {
\NC \V {y}
=\NC \M {Q} \V {h} +\V {z} \NR
}
%
At this stage we would like to apply DS on sparse vectors, as motivated in chapter 1.
However, there is no guarantee that \m {\V {h}} is sparse.

@@

\startsection [title={Spacial frequency domain}]

Introduce the discrete Fourier transform matrix \m {\M {K}}
%
\DispNum {K:K:CN:H1} {
\NC \M {K} \in  \NC \MB {C} ^{N_H \D N_H} \NR
%
\NC \M {K} _{\SB {n_1, n_2}}
= \NC \F {1} {\R {N_H}} \Ss {e}^{2\pi \Ss {i} n_1 n_2 /N_H}, \NR
%
\NC \Q n_1, n_2
= \NC 0, 1, \dots, N_H-1 \NR
}
%
Sans serif \m {\Ss {e}} and \m {\Ss {i}} denote the natural base and imaginary unit, respectively.
Here recall that we have
%
\DispNum {K:K:I:::I} {
\NC \M {K}^\Adj \M {K}
= \NC \M {I} \NR
}
%
Observe that, if we write
%
\DispNum {G:G:KH:HK} {
\NC \M {G}
=\NC \M {K}^\Adj \M {H} \M {K} \NR
}
%
it can be interpreted as spatial frequency domain representation of \m {\M {H}}.
Then
%
\DispNum {Y:Y:WB:NY} {
\NC \M {Y}
=\NC \M {W} _B \M {W} _R \M {K} \D \M {G} \D \M {K}^\Adj \M {F} _R \M {F} _B
+\M {W} _B \M {W} _R \M {Z}
\in \MB {C} ^{N_B \D N_B} \NR
}
%
If it turns out that \m {\M {G}} is sparse, then we may recover \m {\M {G}} instead, justifying the use of DS.
To simplify notation, set
%
\DispNum {P:P:FB:Nh} {
\NC \M {P}
:=\NC \RB {\M {F} _B^\Tr \M {F} _R^\Tr \M {K}^\ast} \otimes \RB {\M {W} _B \M {W} _R \M {K}}
\in \MB {C} ^{N_B^2 \D N_H^2} \NR
}
%
And accordingly
%
\DispNum {g:g:ve:Nh} {
\NC \V {g}
:= \NC \Rm {vec} \SB {\M {G}}
\in \MB {C} ^ {N_H \D N_H} \NR
}
%
Then
%
\DispNum {y:y:Pg:gz} {
\NC \V {y}
=\NC \M {P} \V {g} +\V {z} \NR
}

@@

Our plan now looks like:

\Result
{Algorithm}
{
\startitemize[n]
%
\item Let \m {\g_{\Rm {DS}} \geq 0} be given.
%
\item Input \m {\M {F} _B \in \NC \MB {C} ^{N_R \D N_B}},
\m {\M {F} _R \in \NC \MB {C} ^{N_H \D N_R}},
\m {\M {W} _R \in \NC \MB {C} ^{N_R \D N_H}},
\m {\M {W} _B \in \NC \MB {C} ^{N_B \D N_R}},
and \m {\M {Y} \in \NC \MB {C} ^{N_B \D N_B}}.
%
\item Find \m {\M {P} \in \MB {C} ^{N_B^2 \D N_H^2}}, \m {\V {y} \in \MB {C} ^{N_H^2}} as in above.
%
\item Compute the convex program
%
\DispNum {g:g:mi:DS} {
\NC \Hat {\V {g}}
\LA \NC \startcases
\NC \Min {\V {g}' \in \MB {C} ^{N_H^2}}  \MC \VNm {\V {g}'} _1 \NR
%
\NC \Rm {subject} \; \Rm {to} \Q \MC \VNm {\M {P}^\Adj \RB {\V {y} -\M {P} \V {g}'}} _\infty \leq \g_{\Rm {DS}} \NR
\stopcases \NR
}
%
\item Convert \m {\Hat {\V {g}}} back to the space domain, namely
%
\DispNum {G:G:ve:1g} {
\NC \Hat {G}
\LA \NC \Rm {vec}^{-1} \SB {\Hat {g}} \NR
}
%
\item Recover the estimated \m {\Hat {\M {H}}}, as
%
\DispNum {H:H:KG:GK} {
\NC \Hat {\M {H}}
\LA \NC \M {K} \Hat {\M {G}} \M {K}^\Adj \NR
}
%
\item Output \m {\Hat {\M {H}}}.
%
\stopitemize
}

### 2020-12-16 treatise/4_simulation.tex
New DS narrow figures, OMP square figures

For brevity we shall represent complex vector and matrices by real ones, consisting of its real and imaginary parts.
For \m {\V {x} \in \MB {C} ^{M}}, define the real representation \m {\MS {R} \SB {\V {x}}} of \m {\V {x}} to be
%
\DispNum {R:x:R2:M1} {
\NC \MS {R} \SB {\V {x}}
\in \NC \MB {R} ^{2M} \NR
\NC \MS {R} \SB {\V {x}} _{\SB {m}}
= \NC \startcases
\NC \MF {Re} \SB {\V {x} _{\SB {m'}}}, \MC m =2m' \NR
\NC \MF {Im} \SB {\V {x} _{\SB {m'}}}, \MC m =2m'+1 \NR
\stopcases \NR
\NC m' 
= \NC  0, 1, 2, \ldots, M-1 \NR
}
%
The injection is obvious, and we may define \m {\MS {R} ^{-1}} so that
%
\DispNum {R:1:x::x:} {
\NC \MS {R} ^{-1} \SB {\MS {R} \SB {\V {x}}}
=\NC \V {x} \NR
}
%
Accordingly, the following generalization to complex matrices is valid, once we call the ring representation of complex numbers.
For \m {\M {A} \in \MB {C} ^{M_1 \D M_2}}, define real representation \m {\MS {R} \SB {\M {A}}} of \m {\M {A}} to be
%
\DispNum {R:A:R2:21} {
\NC \MS {R} \SB {\M {A}}
\in \NC \MB {R} ^{2M_1 \D 2M_2} \NR
\NC \MS {R} \SB {\M {A}} _{\SB {m_1,m_2}} =
\NC \startcases
\NC \MF {Re} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC (m_1, m_2) = (2m_1', 2m_2') \NR
\NC \MF {Im} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC (m_1, m_2) = (2m_1'+1, 2m_2') \NR
\NC -\MF {Im} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC (m_1, m_2) = (2m_1', 2m_2'+1) \NR
\NC \MF {Re} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC (m_1, m_2) = (2m_1'+1, 2m_2'+1) \NR
\stopcases \NR
\NC m_1 
= \NC 0, 1, 2, \ldots, M_1 -1 \NR
\NC m_2 
= \NC 0, 1, 2, \ldots, M_2 -1 \NR
}

@@

\Result
{Algorithm}
{
\startitemize[n]
\item Input \m{\M {P} \in \MB {C} ^{ N_B^2 \D N_H^2}}, \m{\V {y} \in \MB {C} ^{ N_B^2}}, \m {\g_{\Rm {DS}} > 0}.
%
\item Define \m {\T {\V {y}}, \T {\V {g}}, \T {\M {P}}, \T {\M {P}} ^\Adj, \T {\V {z}}}, according to \Rf {y:y:Ry:Ny}.
%
\item Calculate
\DispNum {g:f:gf:S1} {
\NC \Hat {\T {\V {g}}}, \Hat {\T {\V {f}}}
\LA \NC \startcases
   \NC \Min {\T {\V {g}}', \T {\V {f}}'}  \MC \IP {\V {1}, \T {\V {f}}'} \NR
   \NC \Rm {subject} \; \Rm {to} \MC \T {\V {g}}' \preceq \T {\V {f}}' \NR
   \NC \MC - \T {\V {g}}' \preceq \T {\V {f}}' \NR
   \NC \MC \T {\M {P}}^\Adj \T {\M {P}} \T {\V {g}}' \preceq \T {\M {P}}^\Adj \T {\V {y}} + \g_{\Ss {DS}} \V {1} \NR
   \NC \MC - \T {\M {P}}^\Adj \T {\M {P}} \T {\V {g}}' \preceq - \T {\M {P}}^\Adj \T {\V {y}} + \g_{\Ss {DS}} \V {1} \NR
\stopcases \NR
}
\item Convert
%
\DispNum {g:::R1:1g} {
\NC \Hat{\V {g}}
\LA \NC \MS {R} ^{-1} \SB {\Hat{\T{\V {g}}}} \NR
}
\item Calculate
%
\DispNum {G:G:ve:1g} {
\NC \Hat {G}
\LA \NC \Rm {vec}^{-1} \SB {\Hat {g}} \NR
}
\item Calculate
%
\DispNum {H:H:KG:GK} {
\NC \Hat {\M {H}}
\LA \NC \M {K} \Hat {\M {G}} \M {K}^\Adj \NR
}
\item Output \m {\Hat {\M {H}}}.
\stopitemize
}

@@

\startsubsection [title={Assorted Plots}]

In the following, we plot the reciprocal of noise level vs relative error norm, for \m {N_H = 8, 12, 16, 20, 24}, respectively.
Figures 3 to 6 have \m {N_H = 3 N_B}, and figures 7 to 10 has \m {N_H = 2 N_B}.

\blank [big]
\externalfigure [assorted-wide-small-error.png] [wfactor=fit, hfactor=fit]
\FigureCaption {Assorted methods, \m {N_H = 3 N_B, N_H = 12}, error.}
\blank [big]
%
\blank [big]
\externalfigure [assorted-wide-medium-error.png] [wfactor=fit, hfactor=fit]
\FigureCaption {Assorted methods, \m {N_H = 3 N_B, N_H = 16}, error.}
%
\blank [big]
\externalfigure [assorted-wide-big-error.png] [wfactor=fit, hfactor=fit]
\FigureCaption {Assorted methods, \m {N_H = 3 N_B, N_H = 20}, error.}
%
\blank [big]
\externalfigure [assorted-wide-very-big-error.png] [wfactor=fit, hfactor=fit]
\FigureCaption {Assorted methods, \m {N_H = 3 N_B, N_H = 24}, error.}
%
\blank [big]
\externalfigure [assorted-narrow-small-error.png] [wfactor=fit, hfactor=fit]
\FigureCaption {Assorted methods, \m {N_H = 2 N_B, N_H = 12}, error.}
\blank [big]
%
\blank [big]
\externalfigure [assorted-narrow-medium-error.png] [wfactor=fit, hfactor=fit]
\FigureCaption {Assorted methods, \m {N_H = 2 N_B, N_H = 16}, error.}
\blank [big]
%
\blank [big]
\externalfigure [assorted-narrow-big-error.png] [wfactor=fit, hfactor=fit]
\FigureCaption {Assorted methods, \m {N_H = 2 N_B, N_H = 20}, error.}
\blank [big]
%
\blank [big]
\externalfigure [assorted-narrow-very-big-error.png] [wfactor=fit, hfactor=fit]
\FigureCaption {Assorted methods, \m {N_H = 2 N_B, N_H = 24}, error.}
\blank [big]

@@

We give one additional plot for extreme low signal level, in order to observe the trend of curves.
\blank [big]
\externalfigure [assorted-medium-low-signal-error.png] [wfactor=fit, hfactor=fit]
\FigureCaption {Assorted methods, \m {N_H = 3 N_B, N_H = 16}, low signal level, error.}
\blank [big]

@@

Again, we plot the reciprocal of noise level vs relative error norm, for \m {N_H = 8, 12, 16, 20, 24}, respectively, and \m {N_H = 3 N_B} for each of them.
Here, \m {\T {\chi}} is shown too.
%
\blank [big]
\externalfigure [ddss-small-error.png] [wfactor=fit, hfactor=fit]
\FigureCaption {DS, \m {N_H = 3 N_B, N_H = 12}, error.}
\blank [big]
%
\blank [big]
\externalfigure [ddss-medium-error.png] [wfactor=fit, hfactor=fit]
\FigureCaption {DS, \m {N_H = 3 N_B, N_H = 16}, error.}
\blank [big]
%
\blank [big]
\externalfigure [ddss-big-error.png] [wfactor=fit, hfactor=fit]
\FigureCaption {DS, \m {N_H = 3 N_B, N_H = 20}, error.}
\blank [big]
%
\blank [big]
\externalfigure [ddss-very-big-error.png] [wfactor=fit, hfactor=fit]
\FigureCaption {DS, \m {N_H = 3 N_B, N_H = 24}, error.}
\blank [big]
%
As for the plot of time taken in minutes, we give only one example of \m {N_H = 16}.
%
\blank [big]
\externalfigure [ddss-medium-time.png] [wfactor=fit, hfactor=fit]
\FigureCaption {DS, \m {N_H = 3 N_B, N_H = 16}, time.}
\blank [big]

@@

%
\blank [big]
\externalfigure [oommpp-small-error.png] [wfactor=fit, hfactor=fit]
\FigureCaption {OMP, \m {N_H = 3 N_B, N_H = 12}, error.}
\blank [big]
%
\blank [big]
\externalfigure [oommpp-medium-error.png] [wfactor=fit, hfactor=fit]
\FigureCaption {OMP, \m {N_H = 3 N_B, N_H = 16}, error.}
\blank [big]
%
\blank [big]
\externalfigure [oommpp-big-error.png] [wfactor=fit, hfactor=fit]
\FigureCaption {OMP, \m {N_H = 3 N_B, N_H = 20}, error.}
\blank [big]
%
\blank [big]
\externalfigure [oommpp-very-big-error.png] [wfactor=fit, hfactor=fit]
\FigureCaption {OMP, \m {N_H = 3 N_B, N_H = 24}, error.}
\blank [big]
%
As for the plot of time taken in minutes, we give only one example of \m {N_H = 16}.
%
\blank [big]
\externalfigure [oommpp-medium-time.png] [wfactor=fit, hfactor=fit]
\FigureCaption {OMP, \m {N_H = 3 N_B, N_H = 16}, time.}
\blank [big]

@@

We want to know the complexity of DS and OMP.
In general, complexity of convex programs is difficult to analyze, in that it is not easily to determine how many iterations were done.
Boyd and Vandenberghe \cite [BoV04] analyzed complexity of inequality constrained Newton method, in which self-concordance is assumed (p.496ff, also p.531).
In our case, Candès and Romberg \cite [CaR05] pointed out that the complex DS can be cast into an second order cone programming (SOCP), and where self concordance holds.
Diamond and Boyd (writers of CVXPY) \cite [DiB16] explained that convex programs are usually converted into primal-dual problems.
The library we called in the simulation is ECOS, where Newton method is used.
Of course, we are not certain there is no method faster than Newton method, and implementation details of CVXPY may change the conclusion too.

>>>>

For brevity we shall represent complex vector and matrices by real ones, consisting of its real and imaginary parts.
For \m {\V {x} \in \MB {C} ^{M}}, define the real representation \m {\MS {R} \SB {\V {x}}} of \m {\V {x}} to be
%
\DispNum {R:x:R2:M1} {
\NC \MS {R} \SB {\V {x}}
\in \NC \MB {R} ^{2M} \NR
\NC \MS {R} \SB {\V {x}} _{\SB {m}}
= \NC \startcases
\NC \MF {Re} \SB {\V {x} _{\SB {m'}}}, \MC m =2m' \NR
\NC \MF {Im} \SB {\V {x} _{\SB {m'}}}, \MC m =2m'+1 \NR
\stopcases \NR
\NC m' 
= \NC  0, 1, 2, \ldots, M-1 \NR
}
%
The injection is obvious, and we may define \m {\MS {R} ^{-1}} so that
%
\DispNum {R:1:x::x:} {
\NC \MS {R} ^{-1} \SB {\MS {R} \SB {\V {x}}}
=\NC \V {x} \NR
}
%
Accordingly, the following generalization to complex matrices is valid, once we call the ring representation of complex numbers.
For \m {\M {A} \in \MB {C} ^{M_1 \D M_2}}, define real representation \m {\MS {R} \SB {\M {A}}} of \m {\M {A}} to be
%
\DispNum {R:A:R2:21} {
\NC \MS {R} \SB {\M {A}}
\in \NC \MB {R} ^{2M_1 \D 2M_2} \NR
\NC \MS {R} \SB {\M {A}} _{\SB {m_1,m_2}} =
\NC \startcases
\NC \MF {Re} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1', 2m_2'} \NR
\NC \MF {Im} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1'+1, 2m_2'} \NR
\NC -\MF {Im} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1', 2m_2'+1} \NR
\NC \MF {Re} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1'+1, 2m_2'+1} \NR
\stopcases \NR
\NC m_1 
= \NC 0, 1, 2, \ldots, M_1 -1 \NR
\NC m_2 
= \NC 0, 1, 2, \ldots, M_2 -1 \NR
}

@@

\Result
{Algorithm}
{
\startitemize[n]
\item Input \m{\M {P} \in \MB {C} ^{ N_B^2 \D N_H^2}}, \m{\V {y} \in \MB {C} ^{ N_B^2}}, \m {\g_{\Rm {DS}} > 0}.
%
\item Define \m {\T {\V {y}}, \T {\V {g}}, \T {\M {P}}, \T {\M {P}} ^\Adj, \T {\V {z}}}, according to \Rf {y:y:Ry:Ny}.
%
\item Compute the convex program
\DispNum {g:f:gf:S1} {
\NC \Hat {\T {\V {g}}}, \Hat {\T {\V {f}}}
\LA \NC \startcases
   \NC \Min {\T {\V {g}}', \T {\V {f}}'}  \MC \IP {\V {1}, \T {\V {f}}'} \NR
   \NC \Rm {subject} \; \Rm {to} \MC \T {\V {g}}' \preceq \T {\V {f}}' \NR
   \NC \MC - \T {\V {g}}' \preceq \T {\V {f}}' \NR
   \NC \MC \T {\M {P}}^\Adj \T {\M {P}} \T {\V {g}}' \preceq \T {\M {P}}^\Adj \T {\V {y}} + \g_{\Ss {DS}} \V {1} \NR
   \NC \MC - \T {\M {P}}^\Adj \T {\M {P}} \T {\V {g}}' \preceq - \T {\M {P}}^\Adj \T {\V {y}} + \g_{\Ss {DS}} \V {1} \NR
\stopcases \NR
}
\item Convert
%
\DispNum {g:::R1:1g} {
\NC \Hat{\V {g}}
\LA \NC \MS {R} ^{-1} \SB {\Hat{\T{\V {g}}}} \NR
}
\item Calculate
%
\DispNum {G:G:ve:1g} {
\NC \Hat {G}
\LA \NC \Rm {vec}^{-1} \SB {\Hat {g}} \NR
}
\item Calculate
%
\DispNum {H:H:KG:GK} {
\NC \Hat {\M {H}}
\LA \NC \M {K} \Hat {\M {G}} \M {K}^\Adj \NR
}
\item Output \m {\Hat {\M {H}}}.
\stopitemize
}

@@

\startsubsection [title={Plots of Assorted Methods}]

In the following, we plot the reciprocal of noise level vs relative error norm, for different values and ratios of \m {N_H} and \m {N_B}.

\blank [big]
\externalfigure [assorted-square-small-error.png] [wfactor=fit, hfactor=fit]
\FigureCaption {Assorted methods, small, \m {N_H = 12, N_B = 12}, error norm.}
\blank [big]
%
\blank [big]
\externalfigure [assorted-square-medium-error.png] [wfactor=fit, hfactor=fit]
\FigureCaption {Assorted methods, medium, \m {N_H = 18, N_B = 18}, error norm.}
\blank [big]
%
\blank [big]
\externalfigure [assorted-square-big-error.png] [wfactor=fit, hfactor=fit]
\FigureCaption {Assorted methods, big, \m {N_H = 24, N_B = 24}, error norm.}
\blank [big]
%
\blank [big]
\externalfigure [assorted-narrow-small-error.png] [wfactor=fit, hfactor=fit]
\FigureCaption {Assorted methods, small, \m {N_H = 12, N_B = 10}, error norm.}
\blank [big]
%
\blank [big]
\externalfigure [assorted-narrow-medium-error.png] [wfactor=fit, hfactor=fit]
\FigureCaption {Assorted methods, medium, \m {N_H = 18, N_B = 15}, error norm.}
\blank [big]
%
\blank [big]
\externalfigure [assorted-narrow-big-error.png] [wfactor=fit, hfactor=fit]
\FigureCaption {Assorted methods, big, \m {N_H = 24, N_B = 20}, error norm.}
%
\blank [big]
\externalfigure [assorted-wide-small-error.png] [wfactor=fit, hfactor=fit]
\FigureCaption {Assorted methods, small, \m {N_H = 12, N_B = 8}, error norm.}
%
\blank [big]
\externalfigure [assorted-wide-medium-error.png] [wfactor=fit, hfactor=fit]
\FigureCaption {Assorted methods, medium, \m {N_H = 18, N_B = 12}, error norm.}
%
\blank [big]
\externalfigure [assorted-wide-big-error.png] [wfactor=fit, hfactor=fit]
\FigureCaption {Assorted methods, big, \m {N_H = 24, N_B = 16}, error norm.}

@@

@@

Again, we plot the reciprocal of noise level vs relative error norm, for \m {N_H = 8, 12, 16, 20, 24}, respectively, and \m {N_H = 3 N_B} for each of them.
Here, \m {\T {\chi}} is shown too.
%
\blank [big]
\externalfigure [ddss-narrow-small-error.png] [wfactor=fit, hfactor=fit]
\FigureCaption {DS, \m {N_B = 10, N_H = 12}, error.}
\blank [big]
%
\blank [big]
\externalfigure [ddss-narrow-medium-error.png] [wfactor=fit, hfactor=fit]
\FigureCaption {DS, \m {N_B = 15, N_H = 18}, error.}
\blank [big]
%
\blank [big]
\externalfigure [ddss-narrow-big-error.png] [wfactor=fit, hfactor=fit]
\FigureCaption {DS, \m {N_B = 20, N_H = 24}, error.}
\blank [big]
%
As for the plot of time taken in minutes, we give only one example of \m {N_H = 18}.
%
\blank [big]
\externalfigure [ddss-narrow-medium-time.png] [wfactor=fit, hfactor=fit]
\FigureCaption {DS, \m {N_B = 15, N_H = 18}, time.}
\blank [big]

@@

%
\blank [big]
\externalfigure [oommpp-square-small-error.png] [wfactor=fit, hfactor=fit]
\FigureCaption {OMP, \m {N_H = N_B = 12}, error.}
\blank [big]
%
\blank [big]
\externalfigure [oommpp-square-medium-error.png] [wfactor=fit, hfactor=fit]
\FigureCaption {OMP, \m {N_H = N_B = 18}, error.}
\blank [big]
%
\blank [big]
\externalfigure [oommpp-square-big-error.png] [wfactor=fit, hfactor=fit]
\FigureCaption {OMP, \m {N_H = N_B = 24}, error.}
\blank [big]
%
As for the plot of time taken in minutes, we give only one example of \m {N_H = 18}.
%
\blank [big]
\externalfigure [oommpp-square-medium-time.png] [wfactor=fit, hfactor=fit]
\FigureCaption {OMP, \m {N_H = N_B = 18}, time.}
\blank [big]

@@

We discuss the complexity of DS and OMP.
In general, complexity of convex programs is difficult to analyze, in that it is not easily to determine how many iterations were done.
Boyd and Vandenberghe \cite [BoV04] analyzed complexity of inequality constrained Newton method, in which self-concordance is assumed (p.496, also p.531).
In our case, Candès and Romberg \cite [CaR05] pointed out that the complex DS can be cast into an second order cone programming (SOCP), and where self concordance holds.
Diamond and Boyd (writers of CVXPY) \cite [DiB16] explained that convex programs are usually converted into primal-dual problems.
The library we called in the simulation is ECOS, where Newton method is used.
Of course, we are not certain there is no method faster than Newton method, and implementation details of CVXPY may change the conclusion too.
